Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-06 appendix.tex
tex

\subsection{Hardness Manipulation (HM)}

@@

As reflected in Sec.~3.1 and Fig.~2, the range of $H(\cdot)$ is $[-2, 2]$.
%
The embedding vectors have been normalized to the real unit hypersphere
as pointed out in the manuscript.
%
And the range of distance between any two points on the hypersphere is
$[0,2]$.
%
Hence
%
\begin{align}
	& \max H(\mA, \mP, \mN)\\
	=& \max [d_\phi(\mA, \mP) - d_\phi(\mA, \mN)]\\
	=& \max [d_\phi(\mA, \mP)] - \min [d_\phi(\mA, \mN)]\\
	=& 2 - 0,
\end{align}
%
\begin{align}
	& \min H(\mA, \mP, \mN)\\
	=& \min [d_\phi(\mA, \mP) - d_\phi(\mA, \mN)]\\
	=& \min [d_\phi(\mA, \mP)] - \max [d_\phi(\mA, \mN)]\\
	=& 0 - 2.
\end{align}
%
Namely $H(\cdot)\in[-2,2]$. Meanwhile, since
%
\begin{equation}
%
L_\text{T}(\mA, \mP, \mN; \gamma) = \max(0, H(\mA, \mP, \mN) + \gamma),
%
\end{equation}
%
we have $L_\text{T}\in[0, 2+\gamma]$.

@@

The only two tunables in HM are $H_\mathsf{S}$ and $H_\mathsf{D}$.
%
They are further discussed in the previous section in this supplementary
material (see the ``Performance-Sensitive Factors'' part of the previous
section).

Since PGD~\cite{madry} is adopted for optimizing the objective of HM, the
PGD parameters (including perturbation budget $\varepsilon$, maximum step
$\eta$, as well as step size $\alpha$) will also influence the result.
%
We following the parameter setting following the state-of-the-art
defense~\cite{robrank} for fair comparison.

	 fix the anchor like ACT?
		not quite helpful. not necessary.

@@

	 why experiment, 8 step by default

>>>>

\subsection{Hardness Manipulation (HM)}
\label{sec:b2}

@@

As reflected in Sec.~3.1 and Fig.~2, the range of $H(\cdot)$ is $[-2, 2]$.
%
The embedding vectors have been normalized to the real unit hypersphere
as pointed out in the manuscript.
%
And the range of distance between any two points on the hypersphere is
$[0,2]$.
%
Hence the extreme values are:
%
\begin{align}
	& \max H(\mA, \mP, \mN)\\
	=& \max [d_\phi(\mA, \mP) - d_\phi(\mA, \mN)]\\
	=& \max [d_\phi(\mA, \mP)] - \min [d_\phi(\mA, \mN)]\\
	=& 2 - 0,
\end{align}
%
\begin{align}
	& \min H(\mA, \mP, \mN)\\
	=& \min [d_\phi(\mA, \mP) - d_\phi(\mA, \mN)]\\
	=& \min [d_\phi(\mA, \mP)] - \max [d_\phi(\mA, \mN)]\\
	=& 0 - 2.
\end{align}
%
Namely $H(\cdot)\in[-2,2]$. Meanwhile, since
%
\begin{equation}
%
L_\text{T}(\mA, \mP, \mN; \gamma) = \max(0, H(\mA, \mP, \mN) + \gamma),
%
\end{equation}
%
we have $L_\text{T}\in[0, 2+\gamma]$.

@@

The only two adjustable items in HM are $H_\mathsf{S}$ and $H_\mathsf{D}$.
%
They are further discussed in the previous section in this supplementary
material (see the ``Performance-Sensitive Factors'' part of the previous
section).

Since PGD~\cite{madry} is adopted for optimizing the objective of HM, the
PGD parameters (including perturbation budget $\varepsilon$, maximum step
$\eta$, as well as step size $\alpha$) will also influence the result.
%
We use the parameter setting following the state-of-the-art
defense~\cite{robrank} for fair comparison.

In most experiments that demonstrate the effectiveness of our method, the
$\eta$ is set as $8$ because the ERS start to plateau with a larger $\eta$
according to our observation.

~\newline
\noindent\textbf{III. HM and ACT}

ACT~\cite{robrank} is proposed in order to address the ``misleading gradient''
and ``inefficient mini-batch exploitation'' problems.
%
HM does not push the embeddings towards arbitrary directions, and hence does
not suffer from both issues.
%
On the other hand, ACT does not perturb the anchor sample, and the same
can be done in HM.
%
When the anchor sample is unperturbed, adversarial training with HM leads to
a higher performance on benign examples but a lower robustness.
%
Unlike perturbing $(\mA, \mP, \mN)$ altogether, only perturbing $(\mP, \mN)$
leads to a weaker adversarial examples, and hence lower robustness.
%
Our first priority is to improve model robustness, so the case with fixed
anchor is omitted from manuscript to avoid complexity.

~\newline
\noindent\textbf{IV. Mixing HM[$\mathcal{R},\mathcal{M}$] and
HM[$\mathcal{S},\mathcal{M}$]}

@@
